\newglossaryentry{colab}
{
    name=Colab,
    description={Colaboratory, or “Colab” for short, is a product from Google Research. Colab allows anybody to write and execute arbitrary python code through the browser, and is especially well suited to machine learning, data analysis and education.}
}
\newglossaryentry{jupyter}
{
    name=Jupyter Notebook,
    description={open-source web application that allows you to create and share documents that contain live code, equations, visualizations and narrative text. Uses include: data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, and much more}
}

\newglossaryentry{anaconda}
{
    name=Anaconda,
    description={Anaconda is a distribution of the Python and R programming languages for scientific computing, that aims to simplify package management and deployment. The distribution includes data-science packages suitable for Windows, Linux, and macOS}
}

\newglossaryentry{virtual machine}
{
    name=Virtual Machine,
    description={In computing, a virtual machine is an emulation of a computer system. Virtual machines are based on computer architectures and provide functionality of a physical computer. Their implementations may involve specialized hardware, software, or a combination}
}

\newglossaryentry{keras}
{
    name=Keras,
    description={Keras is an open-source software library that provides a Python interface for artificial neural networks. Keras acts as an interface for the TensorFlow library. Up until version 2.3 Keras supported multiple backends, including TensorFlow, Microsoft Cognitive Toolkit, R, Theano, and PlaidML}
}

\newglossaryentry{Scikit-learn}
{
    name=Scikit-learn,
    description={is a free software machine learning library for the Python programming language.It features various classification, regression and clustering algorithms including support vector machines, random forests, gradient boosting, k-means and DBSCAN, and is designed to interoperate with the Python numerical and scientific libraries NumPy and SciPy}
}

\newglossaryentry{kaggle}
{
    name=Kaggle,
    description={a subsidiary of Google LLC, is an online community of data scientists and machine learning practitioners}
}

\newglossaryentry{dataset}
{
    name=Dataset,
    description={A data set is a collection of data. In the case of tabular data, a data set corresponds to one or more database tables, where every column of a table represents a particular variable, and each row corresponds to a given record of the data set in question}
}


%\newacronym{}{}{}
